Implementing simplified INLA into `aghq`

### 2022-10-26 src/dev_sinla/sinla.Rmd
Fix KS bug, add distributions and KS plot to script version

samples_laplace <- lapply(1:1:dat$n, function(i) {
  samples <- approxfun(laplace_df$cdf, laplace_df$theta)(runif(M))
  data.frame("value" = samples)
}) %>%
  bind_rows(.id = "index")
```

>>>>

samples_laplace <- lapply(1:dat$n, function(i) {
  laplace_df_i <- filter(laplace_df, index == i)
  samples <- approxfun(x = laplace_df_i$cdf, y = laplace_df_i$theta, ties = "ordered")(runif(M))
  data.frame("value" = samples)
}) %>%
  bind_rows(.id = "index")
```
